The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-03-20 abstract.tex
Typesetting: title and authors

\textbf{The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum}

J. Seguinot\textsuperscript{1},
C. Khroulev\textsuperscript{2},
I. Rogozhina\textsuperscript{3},
A. P. Stroeven\textsuperscript{1},
and Q. Zhang\textsuperscript{1}

>>>>

\textbf{The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum}

J.~Seguinot\textsuperscript{1},
C.~Khroulev\textsuperscript{2},
I.~Rogozhina\textsuperscript{3},
A.~P.~Stroeven\textsuperscript{1},
and Q.~Zhang\textsuperscript{1}

### 2014-03-20 cordillera-climate.tex
Typesetting: title and authors

% ----------------------------------------------------------------------
\begin{document}
% ----------------------------------------------------------------------

% Title
\title{The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum}
\runningtitle{Climate forcing for Cordilleran ice sheet simulations}

% Authors
\author[1]{Julien Seguinot}
\author[2]{Constantine Khroulev}
\author[3]{Irina Rogozhina}
\author[1]{Arjen P. Stroeven}
\author[1]{Qiong Zhang}
\runningauthor{J. Seguinot et al.}
\correspondence{J. Seguinot\\ (julien.seguinot@natgeo.su.se)}

@@

% Title
\maketitle

>>>>

% ----------------------------------------------------------------------
\begin{document}\hack{\sloppy}
% ----------------------------------------------------------------------

% Title
\title{The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum}
\runningtitle{Climate forcing for Cordilleran ice sheet simulations}

% Authors
\author[1]{J.~Seguinot}
\author[2]{C.~Khroulev}
\author[3]{I.~Rogozhina}
\author[1]{A.~P.~Stroeven}
\author[1]{Q.~Zhang}
\runningauthor{J.~Seguinot et~al.}
\correspondence{J.~Seguinot (julien.seguinot@natgeo.su.se)}

@@

% Title
\firstpage{1}
\maketitle
